TR Invariant T.I.

### 2017-04-10 Notes of various papers/TR invariant topological insulators T. Hughes. Dissertation/note.tex
[minor] New calculation in open-boundaries.

    \subsection{Why I think the Lattice Model is wrong}

@@

\subsection{Calculation Note unrelated to the main-subject}

@@

\printnomenclature
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}

>>>>

    \subsection{Why I think the Lattice Model Hamiltonian is mildly wrong}
    \label{sec:Why-LatticeM-m-wrong}

@@

    \subsection{Calculation Note I (Not related to the main discussion)}

@@

\printnomenclature

\subsection{Numerical Solution with open boundary condition in both
dimensions}
\label{sec:nsol-open-bc-inXY}

\textbf{Note 1}: Since the essential point is not altered by the minor
error in Hamiltonian, as mentioned in
Section~\ref{sec:Why-LatticeM-m-wrong}. I will continue with the
Lattice Model Hamiltonian that produce correctly the Dirac Hamiltonian
in the continuum limit.

\textbf{Note 2}: Calculation in this part is available in the
Mathematica notebook "\texttt{Lattice Dirac Model (2+1)-d-2.nb}".

When the two sides are of open boundary, the problem is quite simple
and the Fourier-transformed Hamiltonian is (almost) diagonal in
momentum space. It is (as calculated in \cite{Hughes2009}, eq.2.21):
\begin{align}
    &H =\sum_{p_x,p_y} c^\dagger_{p_x,p_y}\times
    \nonumber\\
    &
    \left[
        \sin(p_x)\sigma^x + \sin(p_y)\sigma^y
        +(2-m-\cos(p_x)-\cos(p_y))\sigma^z
    \right] c_{p_x,p_y}
\end{align}

The eigenvalues of the Hamiltonian of the form
$\vb{a}\vdot\vb{\sigma}$ are:
\begin{equation}
    E_1 = \abs{a},\quad E_2 = -\abs{a}
\end{equation}
If plotted in $(p_x,p_y)$ plane, we will find several interesting
crossing happening when $m=0,2,4$:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m0.pdf}
    \caption{$m=0$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m2.pdf}
    \caption{$m=2$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/E-m4.pdf}
    \caption{$m=4$}
\end{figure}

The eigenvectors are of the form:
\begin{equation}
    \begin{pmatrix}
        \phi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix},\quad \begin{pmatrix}
        \psi, \sin(p_x)+i\cos(p_y)
    \end{pmatrix}
\end{equation}
where
\begin{align}
    \phi &=  (2-m-\cos(p_x)-\cos(p_y))+E_1 \\
    \psi &=  (2-m-\cos(p_x)+\cos(p_y))+E_1
\end{align}
And the have very interesting behavior from $m=-1$ to $m=6$, they
gradually contact and exchange the position of each other
\footnote{You would get more fun if you execute the animation inside
the Mathematica notebook}:
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-mN1.pdf}
    \caption{$m=-1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m0.pdf}
    \caption{$m=0$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m1.pdf}
    \caption{$m=1$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m2.pdf}
    \caption{$m=2$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m3.pdf}
    \caption{$m=3$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m4.pdf}
    \caption{$m=4$}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/OpenBC-inXY/Eigen-m6.pdf}
    \caption{$m=6$}
\end{figure}

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
\end{document}
